Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-09 be.tex
caption.

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value
  $\zeta_c$ of the wind heating parameter $\zeta \equiv
  \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of
  the flow $\mathcal{B}$ is positive near the break radius for some
  value of $\rs$, calculated for core ($\Gamma=0.1$, dot-dashed line)
  and cusp ($\Gamma=0.8$, solid line) galaxies using
  equation~\eqref{eq:enthAnal}. {\emph Bottom Panel:} Minimum value
  of the stagnation radius for which $\mathcal{B} > 0$ at the break
  radius as a function of $\zeta/\zeta_c < 1$. }
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value
  $\zeta_c$ of the wind heating parameter $\zeta \equiv
  \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of
  the flow $\mathcal{B}$ is positive near the break radius for some
  value of $\rs$, calculated for core ($\Gamma=0.1$, dot-dashed line)
  and cusp ($\Gamma=0.8$, solid line) galaxies using
  equation~\eqref{eq:enthAnal}. {\emph Bottom Panel:} Minimum value
  of the stagnation radius for which $\mathcal{B} > 0$ at the break
  radius as a function of $\zeta/\zeta_c < 1$ for $\rb/\rinf=10$.}
\end{figure}

### 2015-04-09 ms.tex
caption.

It is also possible that many of the \citet{Miller+15} sample of
galactic nuclei are not accreting in steady state.  The value of the
X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
represents a maximum value, which does not for instance account for suppression
of the SMBH accretion rate due to outflows from the accretion disk on
small radial scales (e.g., \citealt{Blandford&Begelman99}).  Furthermore, our SFH-averaged accretion rates are derived using analytic expressions for the stagnation radius that may underpredict the true accretion rate if $\zeta < \zeta_c$, as may occur in massive core galaxies with large break radii.  If the actual radiative efficiency is lower than our fiducial assumption,
then many of the X-ray detections would lie above the predicted value
of $\langle L_X \rangle$ for stable accretion (black line).  In this
case the X-ray detected galaxies experience less heating than
average galaxies of the same mass, and may not be stably accreting at
all.  This is particularly plausible because the \citet{Miller+15} sample includes only early-type galaxies, with older stellar
populations than the average for their black hole mass.

@@

% Due to their
%deeper potential well on scales of the sphere of influence, core galaxies are more likely to possess higher accretion rates and
%potentially be thermally unstable for a fixed wind heating rate than
%cusp galaxies.

>>>>

It is also possible that many of the \citet{Miller+15} sample of
galactic nuclei are not accreting in steady state.  The value of the
X-ray efficiency assumed in the right panel of Figure \ref{fig:miller}
represents a maximum value, which does not for instance account for
suppression of the SMBH accretion rate due to outflows from the
accretion disk on small radial scales (e.g.,
\citealt{Blandford&Begelman99}).  Furthermore, our SFH-averaged
accretion rates are derived using analytic expressions for the
stagnation radius that may underpredict the true accretion rate if
$\zeta < \zeta_c$, as may occur in massive core galaxies with large
break radii.  If the actual radiative efficiency is lower than our
fiducial assumption, then many of the X-ray detections would lie above
the predicted value of $\langle L_X \rangle$ for stable accretion
(green line).  In this case the X-ray detected galaxies experience
less heating than average galaxies of the same mass, and may not be
stably accreting at all.  This is particularly plausible because the
\citet{Miller+15} sample includes only early-type galaxies, with older
stellar populations than the average for their black hole mass.

@@
